Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-18 manuscript/main.tex
Compare vaccine strains with observed and estimated best strains
Adds a figure comparing the vaccine strain selections per timepoint to the
observed closest strain to the future and the models' estimated closest
strain. Also, updates the corresponding Jupyter notebook to resize the image to
so the text annotations don't get cropped from the final image on the right side.

Closes #59.

>>>>

\begin{figure*}[ht]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/vaccine-comparison.png}
  \caption{
    Observed distance to natural A/H3N2 populations one year into the future for each vaccine strain (green) and the observed (blue) and estimated (orange) closest strains to the future at the corresponding timepoints.
    Vaccine strains were assigned to their closest timepoint in the validation or test time periods and their distance to the future was calculated from their amino acid sequences and the frequencies and sequences of the corresponding population one year in the future.
    The estimated closest strain to the future was identified by either the best model in the validation period (mutational load and LBI) or the best model in the test period (titer cross-immunity and mutational load).
  }
  \label{fig:vaccine_comparison}
  \end{center}
\end{figure*}
